A possibilistic valid-time model

### 2011-11-17 ipmu2012/introduction.tex
Some small changes. I'll work on the fuzzy numbers and set evaluation parts next.

First of all, the concept of \emph{time} itself is very complex. Klein~\cite{klein94} studied the concept of time in language and Devos~\cite{devos94} modelled vague temporal expressions by means of fuzzy sets~\cite{zadeh65}. More towards information systems, several proposals have been concerned with the obtaining of theoretical models that allow the representation of time in information systems~\cite{cruyssen97,devos98,Cru97}. Notably, temporal relations between time intervals and to a lesser extent time points, were first studied by Allen~\cite{Allen83}.

@@

To allow information systems to cope with imperfections, many approaches adopt fuzzy sets for the representation of temporal information~\cite{Virant199639,35337,343607,nagypal03,Dubois:jucs_9_9:fuzziness_and_uncertainty_in}, though some other tools, like rough sets~\cite{pawlak95}, have also been used~\cite{Qia09}. The temporal relations studied by Allen were recently fuzzified by several authors~\cite{ohlbach04,nagypal03,schockaert08}.

Next to the issues in temporal modelling, the addition of time to a relational database~\cite{Dyreson1994} leads to several more problems, as the modelling of a time-variant object has an impact on the database consistency. Different models have been proposed \cite{Jensen94,TSQL,Sarda90,Jensen91,Snodgrass84,Nascimento95}, but all of these consider time as a crisp notion. In recent works though, some authors consider the necessity of allowing imprecision in temporal models~\cite{Cru97,624013,fuzz2009,gal01}.

Most of these models use the concepts of fuzzy numbers and fuzzy intervals to represent temporal imprecision and considerable attention has thus been given to the problem of transforming two fuzzy numbers which represent the boundaries of an imprecise time interval into one fuzzy interval representing this interval. There are several proposals for this transformation, but some, like those presented in~\cite{fuzz2009} are misleading.

>>>>

First of all, the concept of \emph{time} itself is very complex. Klein~\cite{klein94} studied the concept of time in language and Devos~\cite{devos94} modelled vague temporal expressions by means of fuzzy sets~\cite{zadeh65}. More towards information systems, several proposals have been concerned with the obtaining of theoretical models that allow the representation of time in information systems~\cite{devos98,Cru97}. Notably, temporal relations between time intervals and to a lesser extent time points, were first studied by Allen~\cite{Allen83}.

@@

To allow information systems to cope with imperfections, many approaches adopt fuzzy sets for the representation of temporal information~\cite{343607,nagypal03,Dubois:jucs_9_9:fuzziness_and_uncertainty_in}, though some other tools, like rough sets, have also been used~\cite{Qia09}. The temporal relations studied by Allen were recently fuzzified by several authors~\cite{ohlbach04,nagypal03,schockaert08}.

Next to the issues in temporal modelling, the addition of time to a relational database~\cite{Dyreson1994} leads to several more problems, as the modelling of a time-variant object has an impact on the database consistency. Different models have been proposed \cite{Jensen91,Snodgrass84,Nascimento95}, but all of these consider time as a crisp notion. In recent works though, some authors consider the necessity of allowing imprecision in temporal models~\cite{Cru97,Garrido2009}.

Most of these models use the concepts of fuzzy numbers and fuzzy intervals to represent temporal imprecision and considerable attention has thus been given to the problem of transforming two fuzzy numbers which represent the boundaries of an imprecise time interval into one fuzzy interval representing this interval. There are several proposals for this transformation, but some, like those presented in~\cite{Garrido2009} are misleading.

### 2011-11-17 ipmu2012/preliminaries.tex
Some small changes. I'll work on the fuzzy numbers and set evaluation parts next.

\subsection{\label{subsec:possibility-theory}Possibility Theory}
Possibility theory, like probability theory, deals with uncertainty about the outcome of an experiment. In probability theory, this uncertainty is caused by the variability in the outcomes, while in possibility theory, the uncertainty is caused by incomplete knowledge on the experiment.

\subsection{\label{subsec:possibilistic-variables}Possibilistic Variables}
A possibilistic variable $X$ over a universe $U$ is defined as a variable taking exactly one value in $U$, but for which this value is (partially) unknown. The possibility distribution $\pi_X$ gives the available knowledge about the value that $X$ takes. For each $u\in U$, $\pi_X(u)$ represents the possibility that $X$ takes the value $u$.

It is important to understand the difference between the following two concepts:
\begin{itemize}
\item
A \emph{possibilistic variable} $X$ is bounded to take only one value , but this value is not known due to incomplete knowledge. 
\item
An \emph{ill-known set}~\cite{Dubois88b}: a possibilistic variable defined over the universe $\Pow(U)$.
\end{itemize}

Note that while a possibilistic variable refers to one (partially) unknown value, an ill-known set is a crisp set but, for some reason, (partially) unknown.

>>>>

\subsection{\label{subsec:possibility-theory}Possibility Theory}
Possibility theory, like probability theory, deals with uncertainty about the outcome of an experiment. In probability theory, this uncertainty is caused by the \emph{variability} in the outcomes, while in possibility theory, the uncertainty is caused by \emph{incomplete knowledge} about the experiment. The quantification of confidence in probability theory is achieved by means of a measure of chance, whereas in possibility theory, possibility and necessity measures are used. In any case, the quantification of confidence in a theory of uncertainty is achieved using a confidence measure\cite{Shafer:1976:AMathematical}.

\begin{definition}
Consider a set of outcomes $\Omega$. Let $\wp(\Omega)$ denote the powerset of $\Omega$ and let $A$ and $B$ be elements of $\wp(\Omega)$. A \emph{confidence measure on $\Omega$} is defined by a function
	\begin{align}
	g : \wp(\Omega) & \rightarrow \left[0,1\right]
	\end{align}
that satisfies
	\begin{align}
	g(\emptyset) &= 0 \\
	g(\Omega) &= 1 	\label{NormalizationProperty} \\
	A \subseteq B &\Rightarrow g(A) \leq g(B) \label{MonotonicityProperty}
	\end{align}
\end{definition}

Both possibility measures and necessity measures are special cases of confidence measures.

\begin{definition}
Consider a confidence measure $\Pi$ on a set of outcomes $\Omega$. Let $J$ be a countable index set and let $\{ A_{j} | j \in J \wedge A_{j} \subseteq \Omega \}$ be a family of elements of $\wp(\Omega)$. $\Pi$ is now a \emph{possibility measure on $\Omega$} if it satisfies:
	\begin{align}
	\Pi\left(\bigcup_{j \in J} A_{j} \right) = \sup_{j \in J} \Pi(A_{j})
	\end{align}
\end{definition}

In this work, the interpretation is as follows. The possibility of an event expresses how plausible the occurrence of the event seems to an observer of the experiment, given the (partial) knowledge of the observer about the experiment.

Information on the possibility of distinct elements of the universe of discourse $\Omega$ can now be given by a \emph{possibility distribution} $\pi$ on $\Omega$, defined by:

\begin{definition}
Consider a possibility measure $\Pi$ on $\Omega$. A \emph{possibility distribution} $\pi$ on $\Omega$ underlying the possibility measure $\Pi$ is then a function defined by:
	\begin{align}
	\pi : \Omega \rightarrow \left[0, 1\right] : \pi(u) = \Pi(\{u\})
	\end{align}
\end{definition}

\begin{definition}
Consider a confidence measure $N$ on a set of outcomes $\Omega$. Let $J$ be a countable index set and let $\{ A_{j} | j \in J \wedge A_{j} \subseteq \Omega \}$ be a family of elements of $\wp(\Omega)$. $N$ is now a \emph{necessity measure} on $\Omega$ if it satisfies:
	\begin{align}
	N\left(\bigcap_{j \in J} A_{j} \right) = \inf_{j \in J} N(A_{j})
	\end{align}
\end{definition}

In this work, the interpretation is as follows. The necessity of an event expresses how necessary the occurrence of the event seems to an observer of the experiment, given the (partial) knowledge of the observer about the experiment.

Possibility and necessity measures are dual in the sense that:

\begin{align}
\forall A \subseteq \Omega : N(A) = 1 - \Pi(\bar{A})
\end{align}

Regarding interpretation, the above can be seen as: the degree to which an event is necessary is the degree to which every other possible event is not plausible.

\subsection{\label{subsec:possibilistic-variables}Possibilistic Variables}
A \emph{possibilistic variable} can intuitively be seen as a variable for which the possible values are described by its possibility distribution\cite{Pon11}.

\begin{definition}
A possibilistic variable $X$ over a universe $U$ is defined as a variable taking exactly one value in $U$, but for which this value is (partially) unknown. The possibility distribution $\pi_X$ on $U$ gives the available knowledge about the value that $X$ takes: for each $u\in U$, $\pi_X(u)$ represents the possibility that $X$ takes the value $u$.
\end{definition}

The exact value a possibilistic variable takes, which is (partially) unknown, is called an \emph{ill-known value} in this work\cite{Dubois88b}.

When a possibilistic variable is defined on the powerset $\Pow(R)$ of some universe $R$, the unique value the variable takes will be a crisp set. In this case, the exact set is off course (partially) unknown, but the available knowledge is given in the form of a possibility distribution on the powerset $\Pow(R)$. This exact value (a crisp set) the variable takes, is now called an \emph{ill-known set}\cite{Dubois88b}.

In this work, an ill-known set will be defined via its start and end point, which will be ill-known values. The correspondences and transitions between these two representations are part of the authors current research.

%It is important to understand the difference between the following two concepts:
%\begin{itemize}
%\item
%A \emph{possibilistic variable} $X$ is bounded to take only one value , but this value is not known due to incomplete knowledge. 
%\item
%An \emph{ill-known set}~\cite{Dubois88b}: a possibilistic variable defined over the universe $\Pow(U)$.
%\end{itemize}

%Note that while a possibilistic variable refers to one (partially) unknown value, an ill-known set is a crisp set but, for some reason, (partially) unknown.
